Latentcor: An R Package for Latent Correlation Estimation

### 2021-06-04 paper/paper.Rmd
commit

The R package *latentcor* provides estimation for latent correlation with mixed data types (continuous, binary, truncated and ternary). Comparing to *MixedCCA*, which estimates latent correlation for canonical correlation analysis, our new package provides a standalone version for latent correlation estimation. Also we add new functionality for latent correlation between ternary/continous, ternary/binary, ternary/truncated and ternary/ternary cases.

@@

# Statement of need
Currently there is no standalone package dealing with latent correlation for mixed data type like we did in *latentcor*. The R package *stats* [@team2013r] have some functionality to calculate different type of correlations (Pearson, Kendall and Spearman). The R package *pcaPP* [@croux2013robust] provides a fast calculation for Kendall's \tau. The R package *MixedCCA* [@yoon2020sparse] have functionality for latent correlation estimation as an intermediate step for canonical correlation analysis on mixed data.
No package deal with latent correlation across mixed data type.

>>>>

The R package *latentcor* provides estimation for latent correlation with mixed data types (continuous, binary, truncated and ternary). Comparing to *MixedCCA*, which estimates latent correlation for canonical correlation analysis, our new package provides a standalone version for latent correlation estimation. Also we add new functionality for latent correlation between ternary/continuous, ternary/binary, ternary/truncated and ternary/ternary cases.

@@

# Statement of need
Currently there is no standalone package dealing with latent correlation for mixed data type like we did in *latentcor*. The R package *stats* [@team2013r] have some functionality to calculate different type of correlations (Pearson, Kendall and Spearman). The R package *pcaPP* [@croux2013robust] provides a fast calculation for Kendall's $\tau$. The R package *MixedCCA* [@yoon2020sparse] have functionality for latent correlation estimation as an intermediate step for canonical correlation analysis on mixed data.
No package deal with latent correlation across mixed data type.
